---
bibliography: C:/Users/Cadena Redes/Documents/Tesis/TESIS ESPANIOL/library.bib
csl: apa.csl
fontsize: 11pt
header-includes:
  - \usepackage{placeins}
  - \usepackage{dcolumn}
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{chngcntr}
  - \onehalfspacing
  - \counterwithin{figure}{section}
  - \counterwithin{table}{section}
  - \DeclareUnicodeCharacter{202F}{\,}
  - \usepackage{multicol}
  - \usepackage{multirow}
  - \usepackage[utf8]{inputenc}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{rotating}
  - \usepackage{amsmath}
  - \usepackage[center]{caption}
  - \usepackage[spanish, activeacute]{babel}
  - \newcommand{\Int}{\int\limits}
  - \newcommand{\thickhat}[1]{\mathbf{\hat{\text{$#1$}}}}
  - \newcommand{\thickbar}[1]{\mathbf{\bar{\text{$#1$}}}}
  - \newcommand{\thicktilde}[1]{\mathbf{\tilde{\text{$#1$}}}}
  - \usepackage{xypic}
  - \usepackage{caption}
  - \usepackage{subcaption}
  - \usepackage[font=small, labelfont=bf] {caption}
linkcolor: black
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
  urlcolor: black
---

```{r include=FALSE}
library(easypackages)
my_packages <- c("tidyverse", "foreign", "broom", "texreg", "xtable", "knitr", "captioner", "margins", "stargazer")
libraries(my_packages)

```

```{r include=FALSE}
knitr::opts_chunk$set(fig.path = "figures/", echo = FALSE, warning = FALSE, message = FALSE)
```


```{r include=FALSE}
load(file = "datos11092017.RData" )
```

\pagenumbering{gobble}
\newpage
```{r child = "002_portada.Rmd"}

```
\pagenumbering{roman}

\newpage
```{r child = "003_extracto.Rmd"}

```


\newpage
\FloatBarrier
```{r child = "004_agradecimientos.Rmd"}

```

\newpage
\FloatBarrier


\pagenumbering{gobble}
\tableofcontents
\setcounter{tocdepth}{4}
\newpage

\listoffigures
\addcontentsline{toc}{section}{Indice de gráficos}

\newpage
\FloatBarrier
```{r child = "005_list_of_tables.Rmd"}

```

\newpage
\FloatBarrier

```{r chidl = "006_list_of_figures.Rmd"}

```


\pagenumbering{arabic}
\newpage
\FloatBarrier
```{r child = "007_intro.Rmd"}
  
```

\newpage
\FloatBarrier
```{r child = "008_capitulo_1.Rmd"}

```

\newpage
\FloatBarrier
```{r child = "009_capitulo_2.Rmd"}

```

\newpage
\FloatBarrier
```{r child = "010_capitulo_3.Rmd"}

```

\newpage
\FloatBarrier
```{r child = "011_capitulo_4.Rmd"}

```

\newpage
\FloatBarrier
```{r child = "012_capitulo_5.Rmd"}

```

\newpage
\FloatBarrier
```{r child = "013_capitulo_6.Rmd"}

```
\newpage
\FloatBarrier
```{r child = "014_conclusiones.Rmd"}

```

\newpage
\FloatBarrier

```{r child = "015_anexos_1.Rmd"}

```

\newpage
\FloatBarrier

```{r child = "016_anexos_2.Rmd"}

```

\newpage


```{r child = "017_references.Rmd"}

```